Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-04 cav2017/cav2017.tex
research question --> experimental goal

Using the state-space models given in Section~\ref{experimental-setup}, 
our experimental evaluation aims to answer two research questions:
%

\todo{Remove RQ2 and only discuss the sanity check in 5.3?}

@@

\item[RQ1] \textbf{(CEGIS)} do the multi-staged verification and abstraction-based
CEGIS generate a FWL digital controller in a reasonable amount of time?

\item[RQ2] \textbf{(sanity check)} are the synthesized controllers sound
and can their stability and safety be confirmed outside of our model?

@@

\todo{Discuss the number of abstraction refinements (inner loop, not the outer one)
  for the 2nd approach?
  Although, if it's always one, I'm not sure how interesting it is.. }
\vskip -0.5cm
The median run-time for our benchmark set is 9.4\,s.  Overall, the average
synthesis time amounts to approximately 15.6\,s.  We consider these times
short enough to be of practical use to control engineers, and thus affirm
RQ1.

@@

The synthesized controllers were confirmed to be safe outside of our model
representation using MATLAB, positively answering RQ2.  A~link to the full
experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote as an Open Virtual Appliance
(OVA).\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}

>>>>

Using the state-space models given in Section~\ref{experimental-setup}, 
our evaluation has the following two experimental goals:
%aims to answer two research questions:
%

%\todo{Remove RQ2 and only discuss the sanity check in 5.3?}

@@

\item[EG1] \textbf{(CEGIS)} Show that multi-staged verification and abstraction-based
CEGIS are able to generate FWL digital controllers in a reasonable amount of time.

\item[EG2] \textbf{(sanity check)} Confirm the
stability and safety of the synthesized controllers outside of our model.

@@

\todo{Discuss the number of abstraction refinements (inner loop, not the outer one)
  for the 2nd approach?
  Although, if it's always one, I'm not sure how interesting it is.. }
\vskip -0.5cm
The median run-time for our benchmark set is 9.4\,s.  Overall, the average
synthesis time amounts to approximately 15.6\,s.  We consider these times
short enough to be of practical use to control engineers, and thus affirm
EG1.

@@

The synthesized controllers were confirmed to be safe outside of our model
representation using MATLAB, achieving EG2.  A~link to the full
experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote as an Open Virtual Appliance
(OVA).\footnote{\url{www.cprover.org/DSSynth/controller-synthesis-cav-2017.tar.gz}}
